### 2018-07-08 latex/results.tex
Defined how many birds dont have NNMT

Analysing the phylogeny of the NAD-recycling enzymes in Metazoa in more detail revealed that not only NamPRT replaced NADA, but in most organisms, especially in Deuterostomes, NamPRT is found together with NNMT (fig.~\ref{fig:phylo_distribution}B). NNMT methylates Nam to methyl-Nam that is in mammals excreted with the urine, thus removing Nam from recycling. NNMT seems to have arisen \textit{de~novo} in the common ancestor of Ecdysozoa and Lophotrochozoa. We were unable to find any \textit{NNMT} gene with considerable\todo{define considerable} similarity in fungi or plants. Even though fungal genes named \textit{NNMT} can be found in databases, these genes show very limited sequence similarities to the \textit{NNMT} of nematodes or deuterostomes. The yeast NNMT protein has meanwhile been shown to be a lysin-protein-methyltransferase \cite{Wlodarski2011}.

Nematodes are the only organisms, where we observed any combination of NADA, NamPRT, and NNMT. In Deuterostomes, the only large clade that possesses only NamPRT and seems to have lost NNMT again are Sauropsida and among them especially birds. The reason why a lot of\todo{be more precise!} bird genomes do not seem to encode NNMT remains unclear, as the distribution is quite scattered (suppl. fig.~S2). The lack of NNMT might be related to the excretion system, as the product of NNMT, methyl-Nam, is in mammals excreted with the urine. There are some Metazoan species for which we could not find NamPRT or NADA, while NNMT was present. We assume that this is due to incomplete genomes in the database, as the distribution of such species is scarce and widely scattered.

>>>>

Analysing the phylogeny of the NAD-recycling enzymes in Metazoa in more detail revealed that not only NamPRT replaced NADA, but in most organisms, especially in Deuterostomes, NamPRT is found together with NNMT (fig.~\ref{fig:phylo_distribution}B). NNMT methylates Nam to methyl-Nam that is in mammals excreted with the urine, thus removing Nam from recycling. NNMT seems to have arisen \textit{de~novo} in the common ancestor of Ecdysozoa and Lophotrochozoa. We were unable to find any \textit{NNMT} gene with considerable \todo{define considerable} similarity in fungi or plants. Even though fungal genes named \textit{NNMT} can be found in databases, these genes show very limited sequence similarities to the \textit{NNMT} of nematodes or deuterostomes. The yeast NNMT protein has meanwhile been shown to be a lysin-protein-methyltransferase \cite{Wlodarski2011}.

Nematodes are the only organisms, where we observed any combination of NADA, NamPRT, and NNMT. In Deuterostomes, the only large clade that possesses only NamPRT and seems to have lost NNMT again are Sauropsida and among them especially birds. The reason why about half of the sequenced bird genomes do not seem to encode NNMT remains unclear, as the distribution is quite scattered (suppl. fig.~S2). The lack of NNMT might be related to the excretion system, as the product of NNMT, methyl-Nam, is in mammals excreted with the urine. There are some Metazoan species for which we could not find NamPRT or NADA, while NNMT was present. We assume that this is due to incomplete genomes in the database, as the distribution of such species is scarce and widely scattered.
